Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-27 2019/NUMTA_Barkalov/Special Issure/article.tex
a lot of minor corrections

\begin{abstract}
This paper considers the constrained global optimization problems, in which the functions are of the “black box” type and satisfy the Lipschitz condition. The algorithms for solving the problems of this class require the use of adequate estimates of the a priori unknown Lipschitz constants for the problem functions. A novel approach presented in this paper is based on a simultaneous use of two estimates of the Lipschitz constant: an overestimated and an underestimated one. The upper estimate provides the global convergence whereas the lower one reduces the number of trials necessary to find the global optimizer with the required accuracy. In this case,  the considered algorithm for solving the constrained problems doesn’t use the ideas of the penalty function method; each constraint of the problem is accounted for separately. The convergence conditions of the proposed algorithm are formulated in the corresponding theorem. The results of the numerical experiments on a series of multiextremal problems with non-convex constraints demonstrating the efficiency of the proposed scheme of dual Lipschitz constant estimates are presented.
\end{abstract}

@@

\section{Introduction}
	In this paper, we consider constrained global optimization problems and the numerical methods for solving problems of this type. Such problems are often encountered in applications (see, for example, the review \cite{Pinter2006}). As a rule, problem functions are defined by a program code, i.e. they are “black-box” functions, for which the computing of the values can be a computationally costly operation since in applied problems it will require  numerical modeling. Any  possibility to estimate reliably the global optimum in the multiextremal problems with “black-box” functions is based fundamentally on the auxiliary assumptions relating the possible values of the problem functions to their known values at the points of the trials already performed.

@@

	Within the framework of our research, an original approach to the minimization of the multiextremal functions with non-convex constraints called the index method of the accounting for the constraints 
	\cite{Strongin2000,Pugliese,Barkalov2002,Strongin2003} 
was used. This approach is based on separate accounting for each constraint of the problem and does not involve the use of the penalty functions. According to the rules of the index method, every iteration called trial at the corresponding point of the search domain includes a sequential checking of the feasibility of the problem constraints at this point. When the first violation of any constraint is found, the trial is terminated (the values of the remaining problem functions are not computed at this point) and the transition to the next iteration point is initiated. This allows solving the problems with partially defined functions. The experimental comparison of the index method of accounting for the constraints and the penalty function method demonstrated the advantages of the index method in terms of the number of iterations and the number of computations of the problem functions \cite{Barkalov2017_1, Barkalov2017_2}.

	Note that the values of the Lipschitz constant for the problem functions are usually not known a priori, which  makes their estimation one of the key problems in the construction of the Lipschitzian optimization methods. The methods utilizing the values of the Lipschitz constant predefined a priori (see, for example, \cite{Piyavskii1972, Shubert1972, Wood1991, Meewella1988, Mladineo1986}) are important in the theoretical aspect, but it is difficult to apply such methods in applied problems (in which the information of the Lipschitz constant values is absent).

@@

		Several typical methods for adaptive estimation of the Lipschitz constant according to the results of the performed search trial are known:
\begin{itemize}[\labelitemii]
  \item global estimate of the constant $L$ in the whole search domain $D$ \cite{Horst1996, Pinter1996, Strongin2000}.
  \item local estimates of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ \cite{Kvasov2003, Sergeyev2010, Sergeyev2016}.
	\item choice of the estimates of the constant $L$ from some set of possible values \cite{Gablonsky2001, Jones1993, Jones2009, Sergeyev2006}.
\end{itemize}

@@

	It is supposed that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_{j}(y), 1 \leq j \leq m$, of the constraints satisfy the Lipschitz condition
\begin{equation}\label{lipschitz_condition}
	\left|g_j(y')-g_j (y'')\right| \leq L_j \|y'-y''\|, \; y', y''\in D, \; 1\leq j \leq m+1.
\end{equation}
with \textit{a priori} unknown constant $L_j, 1\leq j \leq m+1$, and may be multiextremal.

@@

\begin{figure}[h]
	\center{\includegraphics[width=0.7\linewidth]{epsilon_reserved_solution}}
	\caption{$\varepsilon$-reserved solution}
	\label{fig:eps_reserved_solution}
\end{figure}

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1$ may be defined only partly. It means that they are defined and calculable only in the sets 
\begin{equation}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point $y$ being considered is no longer feasible terminates further computations at the point $y$.

	Many well known approaches to solving the multidimensional global optimization problems are based on either explicit or implicit reduction of multidimensional problems to one-dimensional ones (see, for example, the description of methods using the diagonal partitions \cite{Sergeyev2006} or simplicial partitions \cite{Zilinskas2008}). In this paper, we will use the approach based on the dimensionality reduction with the use of the space-filling curve $y(x)$ (the Peano curve). Continuous unambiguous mapping $y(x)$ projecting the interval [0,1] onto an $N$-dimensional hypercube $D$ allows reducing a multidimensional constrained minimization problem in the domain $D$ to a one-dimensional constrained optimization problem in the interval [0,1]
\begin{equation}\label{one_dimensional_problem}
	\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_j(y(x))\leq 0, \; 1 \leq j \leq m\right\},
\end{equation}
The issues of the numerical construction of the Peano space filling curve-type mappings and the corresponding theory were described in detail in \cite{Strongin2000, Sergeyev2013}. Note that the theoretical Peano curve $y(x)$ is a limit object and in practice is replaced by its approximation (called \textit{evolvent}) with predefined precision $2^{-m}$ where the number $m>1$ is a parameter of the construction (the density of the evolvent). In this case, the construction density of the evolvent is determined by the accuracy of the possible practical implementation of the problem solution found. For  illustration, Fig. \ref{fig:evolvent} (a), (b) shows the projections of the interval [0,1] are shown for the mapping $y(x)$ with $N=2$ and $m=4,5$, correspondingly.
\begin{figure}[h]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=4} \\ (a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=5} \\ (b)}
	\end{minipage}
	\caption{Evolvent for $N=2$ and $m=4$ (a), $m=5$ (b)}
	\label{fig:evolvent}
\end{figure}

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian objective function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000, Sergeyev2013}), i.e.
$$
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \; x', x''\in [0,1], \; 1\leq j \leq m+1,
$$
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

	According to (\ref{D_sets}) and (\ref{one_dimensional_problem}), the reduced one-dimensional functions $g_j (y(x)), 1 \leq j \leq m+1$ will also be defined and calculable in the corresponding intervals 
\begin{equation}\label{Q_intervals}
	Q_1=[0,1], \; Q_{j+1}=\left\{x \in Q_j : g_j(y(x)) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
These relations allow introducing a classification of the points $x \in [0,1]$ according to the number $\nu = \nu(x)$ of the constraints calculable at the given point. We will call this number $\nu = \nu(x)$ the \textit{index} of the point $x$. The index can be determined from the conditions 
$$
	g_j(y(x)) \leq 0, \; 1 \leq j \leq \nu-1, \; g_{\nu}(y(x))>0,
$$
where the last inequality is insufficient if $\nu = m+1$.

@@

	In the case when the point $y^k$ is a feasible one, i.e. when $y(x^k) \in Q_(m+1)$, the trial involves checking all constraints and computing the objective function. Here, the value of the index is accepted to be equal to the quantity $\nu = m+1$.

@@

	The value $\psi(x)$ at $\nu(x) \leq m$ matches the value of the left-hand part of the first constraint violated at this point $g_{\nu}(y(x))$ divided by the constant $K_{\nu}$. In the case when $\nu(x) = m+1$ 
$$
	\psi(x)=\frac{\varphi(y(x))-\varphi^\ast}{K_{m+1}}
$$
and, consequently, the set of the points, in which the function $\psi(x)$ turns to zero matches the set of the global minimum points of the problem (\ref{one_dimensional_problem}). It should be noted that in any subdomain $Q_j$ the function $\psi(x)$ has the H\"{o}lder coefficient equal to 1.

@@

\section{Index-Based Global Search Algorithm}
	The index-based global search algorithm under consideration for solving the problem (\ref{problem}) (here it is given according to \cite{Strongin2000}) involves the construction of a sequence of points $x^k \in (0,1)$, at which the search trials are conducted with the results of the type (\ref{trial_result}). The set of triplets $\{x^k, z^k=g_{\nu}\big(y(x^k)\big), \nu=\nu(x^k)\}, 1 \leq k \leq n$  makes up the search information accumulated by the method after performing $n$ steps. The operation of the index-based global search algorithm is defined by the following rules.

	The first trial is executed at an arbitrary internal point $x^1 \in (0,1)$. The selection of the point $ x^{k+1}, k \geq 1$, of any next trial is determined by the following steps. \\
Step 1. Renumber the points $x^1, \ldots, x^k$ of the preceding trials by the lower indices in the increasing order of the coordinate values, i.e.
$$
	0=x_0<x_1<\dots <x_k<x_{k+1}=1,
$$
and juxtapose to them the values $z_i=g_{\nu}\big(y(x_i)\big),\nu=\nu(x_i), 1 \leq i \leq k$, computed at these points. The points $x_0=0$ and $x_{k+1}=1$ are introduced additionally and the values $z_0$ and $z_{k+1}$ are not defined. \\
Step 2. Classify the indices $i, 1 \leq i \leq k$, of the trial points in accordance with the number of the constraints of the problem fulfilled at these points by constructing the sets
$$
	I_\nu =\left\{i:1 \leq i \leq k, \; \nu=\nu(x_i) \right\}, \; 1 \leq \nu \leq m+1,
$$
including the numbers of all points $x_i, 1 \leq i \leq k$ with the same values of $\nu$. The end points $x_0=0$ and $x_{k+1}=1$ are interpreted as the ones having the indices equal to zero. An additional set $I_0=\{0, k+1\}$ corresponds to these points.

	Determine the maximum value of the index 
$$
	M=\max\left\{\nu=\nu(x_i), \; 1 \leq i \leq k \right \}.
$$ \\
Step 3. Compute the current lower bounds
\begin{equation}\label{current_lower_bounds}
	\mu_{\nu} = \max\left\{ \frac{\left|z_i-z_j\right|}{ (x_i - x_j)^{1/N} }, \; i,j \in I_\nu, \; i>j \right\},
\end{equation}
for the unknown H\"{o}lder constants $K_{\nu}$ of the functions $g_{\nu}, 1 \leq \nu \leq m+1$. If the set $I_{\nu}$ includes less than two elements or if $\mu_{\nu}$ appears to be equal to zero, then set $\mu_{\nu}=1$. \\
Step 4. For all nonempty sets $I_{\nu}, 1 \leq \nu \leq m+1$, compute the estimates
\begin{equation}\label{z_estimates}
	z_\nu^\ast = \left\{
   \begin{array}{lr}
     -\epsilon_\nu, & \nu < M,\\
     \min\{ z_i: i\in I_\nu \}, & \nu = M,
   \end{array}
	\right.
\end{equation}
where the nonnegative numbers $(\epsilon_1,\ldots,\epsilon_m )$ are the algorithm parameters. \\
Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1$, compute the \textit{characteristics} $R(i)$:
\begin{equation}\label{R_1}
	R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_\nu^2 \mu_\nu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z_\nu^\ast}{r_\nu \mu_\nu}, \;  \nu=\nu(x_i)=\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_2}
	R(i)=2\Delta_i-4\frac{z_i-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_i)>\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_3}
R(i)=2\Delta_i-4\frac{z_{i-1}-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_{i-1})>\nu(x_i),
\end{equation}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$. The values $r_{\nu} > 1, 1 \leq \nu \leq m+1$, are the parameters of the algorithm. With an appropriate selection of $r_{\nu}$ one can use the product $r_{\nu}\mu_{\nu}$ as an estimate of H\"{o}lder constants $K_{\nu}, 1 \leq \nu \leq m+1$. \\
Step 6. Find the interval $(x_{t-1}, x_t)$ with the maximum characteristic
\begin{equation}\label{MaxR}
	R(t)=\max{\left\{R(i): 1 \leq i \leq k+1\right\}}.
\end{equation} \\
Step 7. Execute the next trial at the middle point of the interval $(x_{t-1}, x_t)$ if the indices of the points $x_{t-1}, x_t$ are not the same, i.e.,
$$
	x^{k+1} = \frac{x_t + x_{t-1}}{2}, \; \nu(x_{t-1}) \neq \nu(x_t).
$$
Otherwise, execute a trial at the point
$$
	x^{k+1} = \frac{x_t+x_{t-1}}{2} + \frac{\mathrm{sign}(z_t-z_{t-1})}{2r_\nu}\left[\frac{\left|z_t-z_{t-1}\right|}{\mu_\nu}\right]^N, \; \nu=\nu(x_{t-1})=\nu(x_t).
$$
The inequality $\Delta_t \leq \epsilon$ can be taken as the termination condition, where $t$ is from (\ref{MaxR}) and $\epsilon>0$ is the predefined accuracy.

>>>>

\begin{abstract}
This paper considers the constrained global optimization problems, in which the functions are of the “black box” type and satisfy the Lipschitz condition. The algorithms for solving the problems of this class require the use of adequate estimates of the a priori unknown Lipschitz constants for the problem functions. A novel approach presented in this paper is based on a simultaneous use of two estimates of the Lipschitz constant: an overestimated and an underestimated one. The upper estimate provides the global convergence whereas the lower one reduces the number of trials necessary to find the global optimizer with the required accuracy. The considered algorithm for solving the constrained problems doesn’t use the ideas of the penalty function method; each constraint of the problem is accounted for separately. The convergence conditions of the proposed algorithm are formulated in the corresponding theorem. The results of the numerical experiments on a series of multiextremal problems with non-convex constraints demonstrating the efficiency of the proposed scheme of dual Lipschitz constant estimates are presented.
\end{abstract}

@@

\section{Introduction}
	In this paper, we consider constrained global optimization problems and the numerical methods for solving problems of this type. Such problems are often encountered in applications (see, for example, the review \cite{Pinter2006}). As a rule, problem functions are defined by a program code, i.e. they are ``black-box'' functions, for which the computing of the values can be a time-consuming operation since in applied problems it will require  numerical modeling. Any  possibility to estimate reliably the global optimum in the multiextremal problems with ``black-box'' functions is based fundamentally on the auxiliary assumptions relating the possible values of the problem functions to their known values at the points of the trials already performed.

@@

	Within the framework of our research, an original approach to the minimization of the multiextremal functions with non-convex constraints called the index method of the accounting for the constraints 
	\cite{Strongin2000,Pugliese,Barkalov2002,Strongin2003} 
was used. This approach is based on separate accounting for each constraint of the problem and does not involve the use of the penalty functions. According to the rules of the index method, every iteration called \textit{trial} at the corresponding point of the search domain includes a sequential checking of the feasibility of the problem constraints at this point. When the first violation of any constraint is found, the trial is terminated (the values of the remaining problem functions are not computed at this point) and the transition to the next iteration point is initiated. This allows solving the problems with partially defined functions. The experimental comparison of the index method of accounting for the constraints and the penalty function method demonstrated the advantages of the index method in terms of the number of iterations and the number of computations of the problem functions \cite{Barkalov2017_1, Barkalov2017_2}.

	Note that the values of the Lipschitz constant for the problem functions are usually not known a priori, which  makes their estimation one of the key problems in the construction of the Lipschitzian optimization methods. The methods utilizing the values of the Lipschitz constant predefined a priori (see, for example, \cite{Piyavskii1972, Shubert1972, Wood1991, Meewella1988, Mladineo1986}) are important in the theoretical aspect, but it is difficult to use such methods in applied problems (in which the information of the Lipschitz constant values is absent).

@@

		Several typical methods for adaptive estimation of the Lipschitz constant according to the results of the performed search trials are known:
\begin{itemize}[\labelitemii]
  \item global estimate of the constant $L$ in the whole search domain $D$ \cite{Strongin2000,Pinter1996,Horst1996}.
  \item local estimates of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ \cite{Kvasov2003, Sergeyev2010, Sergeyev2016}.
	\item choice of the estimates of the constant $L$ from some set of possible values \cite{Jones2009,Jones1993, Gablonsky2001,Sergeyev2006}.
\end{itemize}

@@

	It is supposed that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_{j}(y), 1 \leq j \leq m$, of the constraints satisfy the Lipschitz condition
\begin{equation}\label{lipschitz_condition}
	\left|g_j(y')-g_j (y'')\right| \leq L_j \|y'-y''\|, \; y', y''\in D, \; 1\leq j \leq m+1.
\end{equation}
with a priori unknown constants $L_j, 1\leq j \leq m+1$, and may be multiextremal.

@@

\begin{figure}[h]
	\center{\includegraphics[width=0.7\linewidth]{epsilon_reserved_solution}}
	\caption{$\varepsilon$-reserved solution.}
	\label{fig:eps_reserved_solution}
\end{figure}

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1,$ may be defined only partly. It means that they are defined and computable only in the sets 
\begin{equation}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point $y$ being considered is no longer feasible terminates further computations at the point $y$.

	Many well known approaches to solving the multidimensional global optimization problems are based on either explicit or implicit reduction of multidimensional problems to one-dimensional ones (see, for example, the description of methods using the diagonal partitions \cite{Sergeyev2006} or simplicial partitions \cite{Zilinskas2008}). In this paper, we will use the approach based on the dimensionality reduction with the use of the space-filling curve $y(x)$ (the Peano curve). Continuous unambiguous mapping $y(x)$ projecting the interval [0,1] onto an $N$-dimensional hypercube $D$ allows reducing a multidimensional constrained minimization problem in the domain $D$ to a one-dimensional constrained optimization problem in the interval [0,1]
\begin{equation}\label{one_dimensional_problem}
	\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_j(y(x))\leq 0, \; 1 \leq j \leq m\right\}.
\end{equation}
The issues of the numerical construction of the Peano space filling curve-type mappings and the corresponding theory were described in detail in \cite{Strongin2000, Sergeyev2013}. Note that the theoretical Peano curve $y(x)$ is a limit object and in practice is replaced by its approximation (called \textit{evolvent}) with predefined precision $2^{-m}$, where the number $m>1$ is a parameter (the \textit{density} of the evolvent). The evolvent density is determined by the accuracy of the possible practical implementation of the problem solution found. For  illustration, Fig. \ref{fig:evolvent} (a), (b) shows the projections of the interval [0,1] for the mapping $y(x)$ with $N=2$ and $m=4,5$, correspondingly.
\begin{figure}[h]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=4} \\ (a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=1.0\linewidth]{evolvent_N=2_m=5} \\ (b)}
	\end{minipage}
	\caption{Evolvent for $N=2$ and $m=4$ (a), $m=5$ (b)}
	\label{fig:evolvent}
\end{figure}

	The dimensionality reduction scheme considered here matches a multidimensional problem with Lipschitzian objective function and Lipschitzian constraints to a one-dimensional problem, in which the corresponding functions satisfy the uniform H\"{o}lder condition (see \cite{Strongin2000, Sergeyev2013})
$$
	\left|g_j(y(x'))-g_j(y(x''))\right| \leq K_j \left|x'-x'' \right|^{1/N}, \; x', x''\in [0,1], \; 1\leq j \leq m+1,
$$
where $N$ is the dimensionality of the initial multidimensional problem and the coefficients $K_j$ are related to the Lipschitz constants $L_j$ of the initial problem by the relations
\begin{equation}\label{K_leq_L}
	K_j \leq 2L_j \sqrt{N+3}, \; 1\leq j \leq m+1.
\end{equation}

	According to (\ref{D_sets}) and (\ref{one_dimensional_problem}), the reduced one-dimensional functions $g_j (y(x)), 1 \leq j \leq m+1,$ will also be defined and computable in the corresponding intervals 
\begin{equation}\label{Q_intervals}
	Q_1=[0,1], \; Q_{j+1}=\left\{x \in Q_j : g_j(y(x)) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
These relations allow introducing a classification of the points $x \in [0,1]$ according to the number $\nu = \nu(x)$ of the constraints computable at the given point. We will call this number $\nu = \nu(x)$ the \textit{index} of the point $x$. The index can be determined from the conditions 
$$
	g_j(y(x)) \leq 0, \; 1 \leq j \leq \nu-1, \; g_{\nu}(y(x))>0,
$$
where the last inequality is insufficient if $\nu = m+1$.

@@

	In the case when the point $y^k = y(x^k)$ is a feasible one, i.e. when $x^k \in Q_{m+1}$, the trial involves checking all constraints and computing the objective function. Here, the value of the index is accepted to be equal to the quantity $\nu = m+1$.

@@

	The value $\psi(x)$ at $\nu(x) \leq m$ matches the value of the left-hand side of the first constraint violated at this point $g_{\nu}(y(x))$ divided by the constant $K_{\nu}$. In the case when $\nu(x) = m+1$ 
$$
	\psi(x)=\frac{\varphi(y(x))-\varphi^\ast}{K_{m+1}}
$$
and, consequently, the set of the points, in which the function $\psi(x)$ turns to zero matches the set of the global minimum points of the problem (\ref{one_dimensional_problem}). It should be noted that in any subdomain $Q_j$ the function $\psi(x)$ has the H\"{o}lder coefficient equal to 1.

@@

\section{Index-Based Global Search Algorithm}
	The index-based global search algorithm under consideration for solving the problem (\ref{problem}) (here it is given according to \cite{Strongin2000}) involves the construction of a sequence of points $x^k \in (0,1)$, at which the search trials are conducted with the results of the type (\ref{trial_result}). The set of triplets $\{x^k, z^k=g_{\nu}\big(y(x^k)\big), \nu=\nu(x^k)\}, 1 \leq k \leq n,$  makes up the search information accumulated by the method after performing $n$ steps. The operation of the index-based global search algorithm is defined by the following rules.

	The first trial is executed at an arbitrary internal point $x^1 \in (0,1)$. The selection of the point $ x^{k+1}, k \geq 1$, of any next trial is determined by the following steps. \\
Step 1. Renumber the points $x^1, \ldots, x^k$ of the preceding trials by the lower indices in the increasing order of the coordinate values, i.e.
$$
	0=x_0<x_1<\dots <x_k<x_{k+1}=1,
$$
and juxtapose to them the values $z_i=g_{\nu}\big(y(x_i)\big),\nu=\nu(x_i), 1 \leq i \leq k$, computed at these points. The points $x_0=0$ and $x_{k+1}=1$ are introduced additionally and the values $z_0$ and $z_{k+1}$ are not defined. \\
Step 2. Classify the indices $i, 1 \leq i \leq k$, of the trial points in accordance with the number of the constraints of the problem fulfilled at these points by constructing the sets
$$
	I_\nu =\left\{i:1 \leq i \leq k, \; \nu=\nu(x_i) \right\}, \; 1 \leq \nu \leq m+1,
$$
including the numbers of all points $x_i, 1 \leq i \leq k,$ with the same values of $\nu$. The end points $x_0=0$ and $x_{k+1}=1$ are interpreted as the ones having the indices equal to zero. An additional set $I_0=\{0, k+1\}$ corresponds to these points.

	Determine the maximum value of the index 
$$
	M=\max\left\{\nu=\nu(x_i), \; 1 \leq i \leq k \right \}.
$$ \\
Step 3. Compute the current lower bounds
\begin{equation}\label{current_lower_bounds}
	\mu_{\nu} = \max\left\{ \frac{\left|z_i-z_j\right|}{ (x_i - x_j)^{1/N} }, \; i,j \in I_\nu, \; i>j \right\}
\end{equation}
for the unknown H\"{o}lder constants $K_{\nu}$ of the functions $g_{\nu}, 1 \leq \nu \leq m+1$. If the set $I_{\nu}$ includes less than two elements or if $\mu_{\nu}$ appears to be equal to zero, then set $\mu_{\nu}=1$. \\
Step 4. For all nonempty sets $I_{\nu}, 1 \leq \nu \leq m+1$, compute the estimates
\begin{equation}\label{z_estimates}
	z_\nu^\ast = \left\{
   \begin{array}{lr}
     -\epsilon_\nu, & \nu < M,\\
     \min\{ z_i: i\in I_\nu \}, & \nu = M,
   \end{array}
	\right.
\end{equation}
where the nonnegative numbers $(\epsilon_1,\ldots,\epsilon_m )$ are the algorithm parameters. \\
Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1$, compute the \textit{characteristics} $R(i)$:
\begin{equation}\label{R_1}
	R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_\nu^2 \mu_\nu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z_\nu^\ast}{r_\nu \mu_\nu}, \;  \nu=\nu(x_i)=\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_2}
	R(i)=2\Delta_i-4\frac{z_i-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_i)>\nu(x_{i-1}),
\end{equation}
\begin{equation}\label{R_3}
R(i)=2\Delta_i-4\frac{z_{i-1}-z_\nu^\ast}{r_\nu \mu_\nu}, \; \nu=\nu(x_{i-1})>\nu(x_i),
\end{equation}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$. The values $r_{\nu} > 1, 1 \leq \nu \leq m+1$, are the parameters of the algorithm. With an appropriate selection of $r_{\nu}$ one can use the product $r_{\nu}\mu_{\nu}$ as an estimate of H\"{o}lder constants $K_{\nu}, 1 \leq \nu \leq m+1$. \\
Step 6. Find the interval $(x_{t-1}, x_t)$ with the maximum characteristic
\begin{equation}\label{MaxR}
	R(t)=\max{\left\{R(i): 1 \leq i \leq k+1\right\}}.
\end{equation} \\
Step 7. Execute the next trial at the middle point of the interval $(x_{t-1}, x_t)$ if the indices of the points $x_{t-1}, x_t$ are not the same, i.e.,
$$
	x^{k+1} = \frac{x_t + x_{t-1}}{2}, \; \nu(x_{t-1}) \neq \nu(x_t).
$$
Otherwise, execute a trial at the point
$$
	x^{k+1} = \frac{x_t+x_{t-1}}{2} + \frac{\mathrm{sign}(z_t-z_{t-1})}{2r_\nu}\left[\frac{\left|z_t-z_{t-1}\right|}{\mu_\nu}\right]^N, \; \nu=\nu(x_{t-1})=\nu(x_t).
$$
The inequality $\Delta_t \leq \epsilon$ can be taken as the termination condition, where $t$ is from (\ref{MaxR}) and $\epsilon>0$ is the predefined accuracy.

	The convergence conditions for the index global search algorithm can be formulated in the form of the following theorem from \cite{Strongin2000}. 
\\
\textbf{Theorem}. Assume that the following conditions are satisfied:
\begin{enumerate} 
  \item Problem (\ref{problem}) has an $\varepsilon$-reserved solution $y_{\varepsilon}$ from (\ref{epsilon_reserved_solution}).
  \item Functions $g_j(y), 1 \leq j \leq m+1,$ admit Lipschitzian (with the constants $L_j$) extensions $G_{j}(y)$ over the whole feasible domain $D$ from (\ref{D}), i.e.
$$
	g_j \left( y(x) \right) = G_j \left( y(x) \right), \; x \in Q_j, \; 1 \leq j \leq m+1,
$$
where the sets $Q_j$ are from (\ref{Q_intervals}), and $y(x)$ is the curve from (\ref{one_dimensional_problem}).
	\item The parameters of the method $\epsilon_{\nu}, 1 \leq \nu \leq m,$ used in the rule (\ref{z_estimates}) are the corresponding components of the reserve vector $\epsilon_{R}$ from (\ref{epsilon_reserved_solution}).
	\item For a sufficiently large iteration number $k$, the values $\mu_{\nu}$ from (\ref{current_lower_bounds}) satisfy the inequalities
		\begin{equation}\label{theorem_inequalities}
			r_{\nu}\mu_{\nu} > 2^{3-\frac{1}{N}}L_{\nu}\sqrt{N+3}, \; 1 \leq \nu \leq m+1. 
		\end{equation}
Then, any limit point $\bar{y}$ of the sequence of the trials $\{y^k\}=\big\{y\big(x^k\big)\big\}$ generated by the index algorithm for problem (\ref{problem}) belongs to the set $Y_{\epsilon}$ form (\ref{Y_epsilon}) and satisfies the conditions	
$$
	\varphi(\bar y) = \inf\left\{\varphi(y^k):g_j(y^k) \leq 0, 1 \leq j \leq m, k = 1,2,\ldots \right\} \leq \varphi(y_{\epsilon}).
$$
\end{enumerate}
\textbf{Note 1}. The computational scheme of the algorithm is described in the form convenient for  formulating its theoretical properties. The software implementation of this scheme may be made more frugal. For example, according to Step 7, the point $x^{k+1}$ of the next trial will be an internal point of the interval $(x_{t-1}, x_t)$, i.e. $x^{k+1} \in (x_{t-1}, x_t)$. Therefore, the set of trial points $x^1,\ldots, x^k$ (and the related trial results (\ref{trial_result})) may not be ordered  at every step of the algorithm but may be maintained in an ordered state using appropriate data structures.
\\
\textbf{Note 2}. The use of the set of parameters $\epsilon_1,\ldots,\epsilon_m$ (the values of which correspond to the coordinates of the reserve vector $\epsilon_R$) in the index algorithm will significantly reduce the density of the trial sequence in the vicinity of the feasible domain boundaries. However, this raises a question about the particular values of the reserve vector components $\epsilon_R$. In \cite{Strongin2000}, it was proposed to choose the components of the vector $\epsilon_R$ according to the formula 
\begin{equation}\label{epsilon_nu}
	\epsilon_{\nu} = \mu_{\nu}\delta, \; 1 \leq \nu \leq m, 
\end{equation}
where $\mu_{\nu}$ are the current estimates from (\ref{current_lower_bounds}) and $\delta>0$ is a parameter. This approach to choosing the reserve vector components allows one to take into account the properties of different problem functions characterized by their Lipschitz constants. This method for choosing the reserve vector was used in the numerical experiments, the results of which are presented below.
\\
\textbf{Note 3}. The index algorithm for solving the constrained problems is based on the information-statistical algorithm of global search (AGS) for solving unconstrained problems. AGS has been compared repeatedly with both deterministic and nature-inspired global optimization algorithms. The results of the experimental comparison (see, for example, \cite{Sovrasov2019}) show that AGS is superior to many known methods of similar purpose, including DIRECT and DIRECT\textit{l}.
